### 2024-06-25 basic-statistics.qmd
20240624 - chi-square goodness-of-fit test

```{r}
power <- .8
effectSize_d <- .5
effectSize_r <- .24
effectSize_f <- .25
effectSize_fSquared <- .06
```

@@

@@

>>>>

```{r}
power <- .8
effectSize_d <- .5
effectSize_r <- .24
effectSize_f <- .25
effectSize_fSquared <- .06
effectSize_omega <- .3
```

@@

```{r}
pwr::pwr.chisq.test(
  N = N,
  w = effectSize_omega,
  df = numCategories - 1,
  sig.level = alpha)
```

```{r}
pwr::pwr.chisq.test(
  w = effectSize_omega,
  power = power,
  df = numCategories - 1,
  sig.level = alpha)
```

```{r}
pwr::pwr.chisq.test(
  N = N,
  power = power,
  df = numCategories - 1,
  sig.level = alpha)
```

@@

```{r}
pwr::pwr.chisq.test(
  N = N,
  w = effectSize_omega,
  df = (numRows - 1)*(numColumns - 1),
  sig.level = alpha)
```

```{r}
pwr::pwr.chisq.test(
  w = effectSize_omega,
  power = power,
  df = (numRows - 1)*(numColumns - 1),
  sig.level = alpha)
```

```{r}
pwr::pwr.chisq.test(
  N = N,
  power = power,
  df = (numRows - 1)*(numColumns - 1),
  sig.level = alpha)
```
